---
output: html_document
editor_options: 
  chunk_output_type: console
---
`r if(knitr:::is_latex_output()) '\\appendix'`

`r if(!knitr:::is_latex_output()) '# (APPENDIX) Appendix {-}'` 

# Appendix  

The appendix is composed by 3 units, A1 appendix provides complementary tables with information regarding the items and countries used in the analysis.   
Appendix A2 include detailed output for the analysis performed in this research, here can be found the individual model fit statistics LCA by country for different number of classes for both scales studied. Plots for the response categories probabilities and class size for the final selected global model are included as well with the thresholds and the class sizes for the confirmatory global model.  
Finally, appendix A3 includes the syntax used in R to perform the automation of the procedures with MplusAutomation and to provide tables and plot to report results. Mplus syntax used to perform Latent Class Analysis with complex data, along with the different multigroup models to test the level of invariance and the confirmatory model for the global sample are also included in this appendix.    

## Complementary tables  


```{r tableA1, echo=FALSE, warning=FALSE, message=FALSE, results="asis", fig.cap="left-aligned"}
#orScalesIMM <- c("ES3G04A", "ES3G04B", "ES3G04C", "ES3G04D", "ES3G04E")
orScalesGND <- c("IS3G24A", "IS3G24B", "IS3G24E")
orScalesinvGND <- c("IS3G24C", "IS3G24D", "IS3G24F")#, "IS3G24G")

orScalesETH <- c("IS3G25A", "IS3G25B","IS3G25C","IS3G25D", "IS3G25E")

or1ScalesETH <- c("IS3G25A", "IS3G25B")
or2ScalesETH <- c("IS3G25C")
or3ScalesETH <- c("IS3G25D", "IS3G25E")

Scales <- c(orScalesGND, orScalesinvGND, orScalesETH)

labelsScales <- NULL
for(i in 1:length(Scales)){
  labelsScales <- c(labelsScales, ifelse(Scales[i] %in% or1ScalesETH , 
                             paste0("All ethnic and racial groups ",
                                    tolower(str_remove(attr(data_model[[Scales[i]]], "variable.label"), 
           "Rights and Responsibilities/Rights and responsibilities/"))),
           ifelse(Scales[i] %in% or2ScalesETH , 
                             paste0(str_remove(attr(data_model[[Scales[i]]], "variable.label"), 
           "Rights and Responsibilities/Rights and responsibilities/"),
           " members of all ethnic and racial groups"),
           ifelse(Scales[i] %in% or3ScalesETH , 
                             paste0("Members of all ethnic and racial groups ",
                                    tolower(str_remove(attr(data_model[[Scales[i]]], "variable.label"), 
           "Rights and Responsibilities/Rights and responsibilities/"))),
           ifelse(Scales[i] %in% orScalesinvGND,
                  paste0(str_remove(attr(data_model[[Scales[i]]], "variable.label"), 
           "Rights and Responsibilities/Roles women and men/"), " (r)"),
           gsub("[][<>]", "", str_remove(attr(data_model[[Scales[i]]], "variable.label"), 
           "Rights and Responsibilities/Roles women and men/|Moving/")))))))
}

items16 <- cbind(Scales, labelsScales) %>% data.frame()

kbl(items16, 
    caption = "Items for students' endorsement of equal rights and opportunities. ICCS 2016", 
    #label = "tableA4",
    escape = FALSE,
    booktabs = TRUE,
    longtable = TRUE, col.names = c("Item", "Description")) %>% 
  column_spec(1, width = "8em") %>%
  column_spec(2, width = "35em") %>%
  kable_styling(bootstrap_options = c("bordered", "hover"), 
                latex_options = c("repeat_header", "HOLD_position"), 
                position = "left", font_size = 11, full_width = FALSE) %>% 
  #pack_rows("Equal rights for immigrants", 1, 5) %>% 
  pack_rows("Gender equality", 1, 6) %>%
  pack_rows("Equal rights for all ethnic and racial groups", 7, 11)

```

\newpage  


```{r tableA2, echo=FALSE, warning=FALSE, message=FALSE, results="asis", fig.cap="left-aligned"}
Country <- c("Belgium (Flemish)", "Bulgaria", "Chile", "Chinese Taipei", "Colombia", "Croatia", "Denmark", "Dominican Republic", " Estonia", "Finland",
             "Hong Kong SAR", "Italy", "Korea, Republic of", "Latvia", "Lithuania", "Malta", "Mexico", "Netherlands", "Norway", "Peru", 
             "Russian Federation", "Slovenia", "Sweden")

Code <- c("BFL", "BGR", "CHL", "TWN","COL","HRV", "DNK", "DOM", "EST", "FIN", "HKG", "ITA", "KOR", "LVA", "LTU", "MLT", "MEX","NLD", "NOR", "PER", "RUS", "SVN", "SWE")

Students <- c(2931,2966,5081,3953,5609,3896,6254,3937,2857,3173,2653,3450,2601,3224,3631,3764,5526,2812,6271,5166,7289,2844,3264)

Schools <- c(162,147,178,141,150,175,184,141,164,179,91,170,93,147,182,47,213,123,148,206,352,145,155)

sample<- data.frame(Code, Country, Schools, Students)
sample %>% 
kbl(caption = "Countries sample sizes that participate in ICCS 2016", 
    #label = "tableA1",
    escape = FALSE, booktabs = TRUE, longtable = TRUE, col.names = c("AlphaCode","Country","Participating schools", "Participating students")) %>% 
  column_spec(1, width = "10em") %>%
  row_spec(c(1,2,6,7,9,10,12,14,15,16,18,19,22,23), bold = TRUE, italic = FALSE) %>% 
  kable_styling(bootstrap_options = c("bordered", "hover"), 
                latex_options = c("repeat_header", "HOLD_position"), 
                position = "left", font_size = 11, full_width = FALSE) %>% 
  footnote(general = "Countries in bold were selected for this research")
```  

\newpage  


\blandscape

## Detailed output

```{r detailed1, ref.label='modelfitcnty1', echo = FALSE}
```

\elandscape

```{r detailedplot1, ref.label='higprob1', echo = FALSE, fig.cap = "Response categories probabilities and class size for 4-classes global model for Attitude towards gender equality scale", fig.width=5, fig.height=4}
```


```{r detailed2, ref.label='cfa1', echo = FALSE}
```


\blandscape

```{r detailed3, ref.label='modelfitcnty2', echo = FALSE}
```

\elandscape

```{r detailedplot2, ref.label='higprob2', echo = FALSE , fig.cap = "Response categories probabilities and class size for 4-classes global model for Attitude towards ethnic and race equal rights scale", fig.width=5, fig.height=4}
```

```{r detailed4, ref.label='cfa2', echo = FALSE}
```

## Syntax

#### R Packages[^1]  

```{r ref.label='include_packages', results='hide', echo = TRUE}

```


[^1]: All codes can be found in https://github.com/PamelaInostroza/Master-s-thesis  

<!-- #### MplusAutomation syntax -->

```{r results='markup', eval=FALSE}
fileName <- 'functions/Create_RunModels.R'
#89780
cat(readChar(fileName, 3318), collapse = "\n")
```

<!-- #### Automatized R code -->

```{r results='markup', eval=FALSE}
fileName <- 'functions/0.functions.R'
#23152
cat(readChar(fileName, 11468), collapse = "\n")
```


```{r results='markup', eval=FALSE}
fileName <- 'functions/code.txt'
cat(readChar(fileName, file.info(fileName)$size), collapse = "\n")
```


#### Mplus syntax  

##### Latent Class model with 4 classes  

\  

```{r mplussyntax1, results='markup', echo = FALSE}
fileName <- 'data/MplusModels/LCA/GND_lca_C3cl4.inp'

cat(readChar(fileName, file.info(fileName)$size), collapse = "\n")
```


##### Complete homogeneous multigroup latent class model with 4 classes

\  

```{r mplussyntax2, results='markup', echo = FALSE}
fileName <- 'data/MplusModels/CountryMG/GND_MGCnty_C3cl4_3CHom.inp'

cat(readChar(fileName, file.info(fileName)$size), collapse = "\n")
```


#### Partial homogeneous multigroup latent class model with 4 classes  

\  

```{r mplussyntax3, results='markup', echo = FALSE}
fileName <- 'functions/PartialMGmpluscode.txt'

cat(readChar(fileName, file.info(fileName)$size), collapse = "\n")
```

#### Complete heterogeneous multigroup latent class model with 4 classes

\  

```{r mplussyntax4, results='markup', echo = FALSE}
fileName <- 'functions/HeterMGmpluscode.txt'

cat(readChar(fileName, file.info(fileName)$size), collapse = "\n")
```

#### Confirmatory latent class model with 4 classes for Students' endorsement of gender equality scale

\  

```{r mplussyntax5, results='markup', echo = FALSE}
fileName <- 'data/MplusModels/LCA/GND_Conflca_C3cl4.inp'

cat(readChar(fileName, file.info(fileName)$size), collapse = "\n")
```

#### Confirmatory latent class model with 4 classes for Students' endorsement of equal rights for all ethnic/racial groups scale

\  

```{r mplussyntax6, results='markup', echo = FALSE}

fileName <- 'data/MplusModels/LCA/ETH_Conflca_C3cl4.inp'

cat(readChar(fileName, file.info(fileName)$size), collapse = "\n")
```

